Exploring Design Space for Differentially Private Bayesian Inference

### 2018-12-28 ICML2019/main.tex
fix bug
update plots

\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $\epsilon$-differential privacy.
\end{lem}

\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.

@@

We consider 6 mechanisms in our comparison, including the Laplace mechanism, improved Laplace mechanism, standard exponential mechanism, non-private exponential mechanism (using local sensitivity) and two newly designed mechanisms (one with smooth sensitivity achieving $(\epsilon, \delta)-$dp and the other with $\gamma$ sensitivity achieving $\epsilon-$dp).

>>>>

\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy}

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $\epsilon$-differential privacy.
\end{lem}
\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.

@@

We consider 5 mechanisms in our comparison experiments, including the Laplace mechanism ($\lapmech$), improved Laplace mechanism ($\ilapmech$), standard exponential mechanism ($\mathsf{expMech}$), non-private exponential mechanism ($\lexpmech$) and the newly designed mechanisms ($\hexpmech$ with $\gamma$ sensitivity achieving $\epsilon-$dp).
